experiment 1

### 2021-08-12 experiments/experiment 1/experiment-1.Rmd
corrected: x2x6 to x1x1

max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
#var_expt_levels[20,]
var_expt_copy <- var_expt
```

@@

@@

```{r eval=FALSE}
## Here the simulations with least and most tolerantsulfur bacteria are run.
var_expt <- var_expt_least_tolerant_SBPB
var_expt_least_tolerant_SBPB <- run_ss_var_experiment()
saveRDS(var_expt_least_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))

var_expt <- var_expt_most_tolerant_SBPB
var_expt_most_tolerant_SBPB <- run_ss_var_experiment()
saveRDS(var_expt_most_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))
```

```{r, fig.height=7.5, fig.width=12}
var_expt_least_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_least_tolerant.RDS"))
var_expt_most_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial_SBPB_most_tolerant.RDS"))

@@

```{r, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[no_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')

plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')

plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[no_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')

plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
                var_expt_copy[max_only_SBPB_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')
```

>>>>

max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
#var_expt_levels[20,]
```

@@

## multiplier of SBPB variation
CB_var_multiplier <- 1
SBPB_var_multiplier <- 1

@@

```{r eval=FALSE}
## Here the simulations with least and most tolerantsulfur bacteria are run.
var_expt <- var_expt_least_tolerant_SBPB
var_expt_least_tolerant_SBPB <- run_ss_var_experiment()
saveRDS(var_expt_least_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_least_tolerant.RDS"))

var_expt <- var_expt_most_tolerant_SBPB
var_expt_most_tolerant_SBPB <- run_ss_var_experiment()
saveRDS(var_expt_most_tolerant_SBPB, here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_most_tolerant.RDS"))
```

```{r, fig.height=7.5, fig.width=12}
var_expt_least_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_least_tolerant.RDS"))
var_expt_most_tolerant_SBPB <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x1x1_factorial_SBPB_most_tolerant.RDS"))

@@

```{r, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)

plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
                var_expt[no_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')

plot_ss_result2(var_expt_least_tolerant_SBPB$ss_res[[1]],
                var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with LEAST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')

plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
                var_expt[no_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with no diversity (average values) (dashed line)')

plot_ss_result2(var_expt_most_tolerant_SBPB$ss_res[[1]],
                var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                xlims = c(-7, -1))+
  plot_annotation(title = 'Sims with MOST tolerant SB and PB strains + average CB strain (solid line)\nVersus\nSims with diversity in SBPB, no diversity (average value) in CB (dashed line)')
```
